Observation of the Torsional Motion of a Solar Jet at the Limb

### 2016-08-15 paper/ms_temp_paper.tex
Some bits

dop_grid = manager.save_figure('dop-exam', fig)
dop_grid.figure_width = r'\textwidth'
dop_grid.placement = 't'
dop_grid.caption = ''

>>>>

dop_grid = manager.save_figure('dop-exam', fig)
dop_grid.figure_width = r'\textwidth'
dop_grid.placement = 't'
dop_grid.caption = 'Above is the result of the dopplergram processing during the evolution of the second ejection of plasma starting at $07:37:00$'
